### 2023-05-24 paper/sec-dis-pseudodata.tex
done intro

\clearpage
\section{Projections for LHC neutrino structure functions}
\label{sec:dis_pseudodata}

We begin by describing the procedure adopted to generate
projections for LHC neutrino DIS structure functions, including
the models for the expected systematic uncertainties associated
to the various experiments.

\subsection{Recap of DIS kinematics}

The double-differential cross-section for neutrino-nucleus scattering
can be decomposed
in terms of three independent structure functions $F_i^{\nu A}(x,Q^2)$ with $i=1,2,3$.
%
Focusing on the charged-current (CC) scattering case, mediated
by the exchange of a $W^+$ weak boson, the differential
 cross section reads
\be
\label{eq:neutrino_DIS_xsec}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2) + y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc  \, ,
\ee
where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
$E_\nu$ is the incoming neutrino energy,
and the inelasticity $y$ is defined as $y=Q^2/(2x m_n E_{\nu})$.
%
For the time being we are neglecting target mass 
corrections.
%
An analogous expression holds for  antineutrino 
scattering, mediated
by the exchange of a $W^-$ weak boson, with the only difference being a sign change
in front of the parity-violating structure function $xF_3$,
\be
\label{eq:antineutrino_DIS_xsec}
\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\bar{\nu} A}_2(x,Q^2) + y^2xF^{\bar{\nu} A}_1(x,Q^2) - y\lp 1-\frac{y}{2}\rp xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, .
\ee
While the differential cross-section depends on three kinematic variables, $(x,Q^2,y)$,
the structure functions themselves depend only on $x$ and $Q^2$.
%
Furthermore, both the cross-section and the structure functions depend
on the atomic mass number $A$ of the target nucleus via nuclear modifications of the free-nucleon
structure functions.

Alternatively, Eq.~(\ref{eq:neutrino_DIS_xsec}) can be expressed in terms
of the longitudinal structure function  $F_L^{\nu A}(x,Q^2)$ defined
by $F_L = F_2-2xF_1$, leading to
\be
\label{eq:neutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc  \, ,
\ee
where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
\be
\label{eq:antineutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, ,
\ee
%
Expressing the differential cross-section as in Eq.~(\ref{eq:neutrino_DIS_xsec_FL}) is advantageous
because in the parton model (and in perturbative QCD at leading order) the longitudinal
structure function vanishes, $F_L^{\nu A}(x,Q^2)=0$.
%
The combination of neutrino and antineutrino measurements makes possible disentangling
the different structure functions, for example the cross-section difference
\be
\label{eq:neutrino_DIS_xsec_FL_diff}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} - \frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy}=  \frac{G_F^2s Y_-}
{4\pi \lp 1+Q^2/m_W^2\rp^2}\lc    xF^{\nu A}_3(x,Q^2)+  xF^{\bar{\nu} A}_3(x,Q^2)\rc \, ,
\ee
is proportional to the parity-violating structure function $xF_3$ averaged over neutrinos
and antineutrinos.

When both the momentum transfer squared $Q^2$
and the  hadronic final-state
invariant mass $W$ given by
\be
W^2 = m_N^2 + Q^2 \frac{(1-x)}{x} \, ,
\ee
are large enough, $Q^2 \gsim {\rm few~GeV}^2$ and $W \gsim 2$ GeV
respectively, we find ourselves in the
deep-inelastic scattering region where
structure functions can be evaluated in perturbative QCD in terms of a factorised
convolution of process-dependent partonic scattering cross-sections and
of process-independent parton distribution functions,
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, ,
 \ee
 where $j$ is an index that runs over all possible partonic initial states
 and $C_{i,j}^{\nu N}$ is the process-dependent (but target-independent) coefficient function.
 %
 The latter can be expressed  as a series expansion in powers of the strong
 coupling $\alpha_s(Q^2)$,
 \be
 \label{eq:coeff_fun_expansion}
 C_{i,j}^{\nu N}(z,\alpha_s(Q^2)) = \sum_{k=0}^m \lp \alpha_s(Q^2) \rp^{k} C_{i,j}^{\nu N(k)}(z) \, .
 \ee
 The leading-order ($k=0$)  term is independent of $\alpha_s$ since the Born scattering
 is mediated by the weak interaction.
 %
 At leading order and considering a proton target, $n_f=4$ active quark flavours,
 neglecting charm mass effects and assuming a diagonal CKM matrix,
 we can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
 follows
 \bea
 F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
 xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
 \eea
 The corresponding expressions for a neutron target and or isoscalar target can be obtained
 from isospin symmetry, for instance the LO structure functions for
 neutrino-neutron scattering are
 \bea
 F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs} \\
 xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
 \eea

>>>>

\section{Projections for LHC neutrino structure functions}
\label{sec:dis_pseudodata}

We begin by describing the procedure adopted to generate
projections for DIS structure functions associated to LHC neutrinos.
%
Assembling these projections requires defining the kinematic acceptance
and expected yields of the various ongoing and proposed experiments,
assessing the performance of their response in order to estimate
the corresponding systematic uncertainties,
and then evaluating pseudo-data based on specific underlying theory assumption which should be consistent
with the settings of the subsequent (nuclear) PDF analyses.

In this section, for completeness first of all we provide a recap of the kinematics
of neutrino DIS structure function measurements.
%
Then we present an overview of the LHC far-forward neutrino detectors that
will be considered in the present study.
%
The calculation of event yields in bins of $x,Q^2$, and neutrino energy $E_\nu$ in terms
of the incoming neutrino fluxes is presented next, resulting in quantitative predictions
for the kinematic coverage and statistical uncertainties.
%
Finally, we discuss how for each of the considered experiments the dominant systematic
uncertainties are evaluated and which assumptions are taken about their bin-to-bin correlations.

\subsection{Neutrino deep-inelastic scattering}

The theoretical framework underlying neutrino DIS is well known, see e.g.~\cite{Candido:2023utz}
and references therein.
%
For completeness, we provide here a short overview of the neutrino DIS formalism.
%
The double-differential cross-section for neutrino-nucleus charged-current scattering
can be expressed in terms of three
independent structure functions $F_2^{\nu A}(x,Q^2)$, $xF_3^{\nu A}(x,Q^2)$
and $F_L^{\nu A}(x,Q^2)$ as follows
\be
\label{eq:neutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc  \, ,
\ee
where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
\be
\label{eq:antineutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, ,
\ee
where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
$E_\nu$ is the incoming neutrino energy,
and the inelasticity is $y=Q^2/(2x m_n E_{\nu})$.
%
While structure functions depend only on $x$ and $Q^2$, the differential
cross-section depends also on the neutrino energy $E_\nu$ (or alternatively
on the inelasticity $y$).
%
Structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering
for the neutrino scattering through the nuclear modifications of the proton PDFs.

Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid in the  inelastic
scattering regime, defined as the kinematic region for which the 
hadronic final-state
invariant mass $W$  satisfies
\be
W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
\ee
given that for smaller values of $W^2$  neutrino scattering is dominated by either quasi-elastic scattering
or the resonance production region.
%
Provided the momentum transfer becomes large enough, $Q^2 \gsim {\rm few~GeV}^2$,
the inelastic structure functions Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL})
can be decomposed in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$, 
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
 \ee
 Eq.~(\ref{eq:sfs_pqcd}) holds both for inclusive and for heavy quark production structure functions,
 thought in the latter case one needs to account for mass-dependent effects.
 %
 Neutrino structure functions can be computed up to N$^3$LO for the massless case
 and up to NNLO (with respect to the Born cross-section) for the charm production
 case~\cite{Gao:2017kkx}.
 %
 We discuss in Sect.~\ref{sec:settings} the
 tools~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} used in this work to
 evaluate neutrino DIS structure functions in order to generate
 LHC neutrino pseudo-data.
 %
 In this work we don't consider structure functions in the shallow inelastic scattering region (SIS)
 defined by $Q^2 \lsim {\rm few~GeV}^2$, for which a different approach
 must the  adopted for their evaluation~\cite{Candido:2023utz}.

 Each different structure function provides complementary sensitivity
 to the partonic flavour decompositions of nucleons.
 %
 To illustrate this sensitivity, one can consider a leading order (LO) calculation
 for a proton target, $n_f=4$ active quark flavours,
 neglecting charm mass effects and assuming a diagonal CKM matrix.
 %
 In this scenario one can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
 follows:
 \bea
 F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
 xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
 \eea
 The corresponding expressions for a neutron target are obtained from isospin symmetry
 \bea
 F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs} \\
 xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, , \nonumber
 \eea
 while for an isoscalar, free-nucleon target denoted by $N$ one has
 \bea
 F_2^{\nu N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_s + 2f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_{\bar{s}} + 2f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
 xF_3^{\nu N}(x,Q^2) &=& 2x\lp f_{u^-} + f_{d^-} +2f_s - 2f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} N}(x,Q^2) &=& 2x\lp   f_{u^-} + f_{d^-}-2f_{\bar{s}} +2 f_{c}\rp(x,Q^2) \, , \nonumber
 \eea
 in terms of the valence and sea PDF combinations defined by
 \be
 f_{q^+} (x,Q^2)\equiv \lp f_{q}+f_{\bar{q}}\rp(x,Q^2) \, , \qquad
 f_{q^-} (x,Q^2)\equiv \lp f_{q}- f_{\bar{q}}\rp(x,Q^2) \, .
 \ee
 From this partonic decomposition we see that even for isoscalar targets separate measurements
 for neutrinos and antineutrinos are not equivalent since in general neither $f_{s^-}$ nor
 $f_{c^-}$ are expected to vanish.

 In the projections presented in this work, when interpreting the LHC neutrino structure
 functions in terms of proton PDFs we assume isoscalar free-nucleon targets and neglect
 nuclear PDF modifications.
 %
 When evaluating structure functions for a tungsten (W) target, we keep into account
 that the target is not isoscalar when evaluating the physical observables.

 \subsection{Far-forward neutrino detectors at the LHC}
 \label{sec:neutrinoDetectors}

### 2023-05-24 paper/sec-introduction.tex

The outline of this paper is as follows.
%

>>>>

Proton-proton collisions at energy-frontier hadron colliders
such as the LHC produce an intense collimated flux of neutrinos~\cite{Kling:2021gos}.
%
These neutrinos are characterised by the largest energies ever achieved in laboratory experiments
and reaching up to  several TeV, only surpassed by astrophysical neutrinos.
%
Due to the lack of dedicated instrumentation in the LHC far-forward region,
until recently these neutrinos escaped detection and hence could not be used
for scientific enquiry.
%
This situation changed drastically in  March 2023
with the reports of the first observation of LHC neutrinos~\cite{FASER:2023zcr} by the
far-forward  FASER$\nu$~\cite{FASER:2019dxq} and SND@LHC~\cite{SHiP:2020sos} experiments.
%
The discovery of LHC neutrinos enables
unprecedented scientific opportunities
for particle and astroparticle physics both within the Standard Model and beyond it,
see~\cite{Anchordoqui:2021ghd,Feng:2022inv}
and references therein for a comprehensive summary.
%
Beyond the ongoing Run III, a dedicated suite of upgraded far-forward
neutrino experiments hosted by a dedicated
Forward Physics Facility (FPF)~\cite{Anchordoqui:2021ghd,Feng:2022inv} has been
proposed to operate concurrently with the HL-LHC.

Among its many possible applications, the high-energy neutrino beam produced by the LHC
can be deployed as a sensitive probe of hadron structure.
%
As well known~\cite{Conrad:1997ne,Mangano:2001mj},
measurements of neutrino structure functions in deep-inelastic scattering
(DIS)~\cite{Candido:2023utz} provide valuable information on the parton distribution functions (PDFs)
of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh}, in particular
concerning the quark and antiquark PDF flavour separation.
%
Furthermore, these constraints from charged-current neutrino DIS are complementary to those
provided by neutral-current charged-lepton DIS, being sensitive to independent
flavour combinations.
%
With this motivation, several  experiments have in the past measured neutrino-nucleus
DIS structure functions over a wide range of energies, and neutrino data
from e.g. the CHORUS~\cite{CHORUS:2005cpn}, NuTeV~\cite{NuTeV:2001dfo},
CCFR~\cite{Yang:2000ju}, and CDHS~\cite{Berge:1989hr} experiments enter 
some of the most recent global determinations of proton~\cite{Hou:2019efy,Bailey:2020ooq,NNPDF:2021njg} and
nuclear PDFs~\cite{AbdulKhalek:2022fyi,Eskola:2021nhw,Muzakka:2022wey}.

As compared to previous neutrino DIS measurements,  LHC data benefits
from higher neutrino energies  increasing the kinematic coverage
in the $(x,Q^2)$ plane by an order of magnitude both in the small-$x$
and the large-$Q^2$ directions~\cite{Feng:2022inv}.
%
Furthermore, the large number of expected neutrino scattering events enable
structure function measurements with excellent precision,
e.g. the  $\mathcal{O}(10^6)$ muon neutrinos expected at the FPF detectors~\cite{Kling:2021gos}
enable sub-percent statistical uncertainties for most of the bins in the $(x,Q^2)$ plane.
%
However,  so far discussions about the impact of far-forward LHC neutrinos on hadronic structure
have been restricted to the level  of qualitative estimates.
%
The main reason for this limitation is the lack
of dedicated projections for the LHC neutrino structure function data, including the expected
statistical and systematic uncertainties for the various operating and proposed detectors.

The main goal of this work is to bridge this gap and quantify
the expected impact of LHC neutrino DIS data on the PDFs of  nucleons and heavy nuclei
for the various relevant experiments and for different assumptions about their performance
and the integrated luminosities.
%
In addition to projections for FASER$\nu$ and SND@LHC based on the full Run III luminosity,
we consider also three of the proposed FPF experiments, FLArE, AdvSND, and FASER$\nu$2.
%
For each detector, we generate dedicated  pseudo-data for both inclusive and charm (dimuon)
structure functions and estimate the event yields as a function of the binning
in $x$ and $Q^2$.
%
Emphasis is devoted to assessing the expected systematic uncertainties
from the intended acceptance and performance of the LHC neutrino experiments.

Following this DIS pseudo-data generation, we study their impact first
on the proton PDFs and subsequently on the nuclear PDFs.
%
In the former case, this is achieved both by means of the Hessian profiling~\cite{Paukkunen:2014zia}
of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh} and by means
of their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
%
In the latter case, the EPPS21 global nuclear PDF determination~\cite{Eskola:2021nhw}
is profiled again using {\sc\small xFitter}.
%
Theoretical predictions for neutrino DIS structure functions are evaluated with the {\sc\small EKO}~\cite{Candido:2022tld}
and {\sc\small YADISM}~\cite{yadism,Candido:2023utz} programs interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}, with the latter providing the fast interpolation grids to be used in the fit.
%
To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed.

Qualitatively consistent results are obtained from the analyses using both the {\sc\small xFitter}
and NNPDF frameworks and reveal that  LHC neutrino scattering, specially
for the high-statistics  experiments of the FPF, provides  stringent constraints
disentangling the quark and antiquark (nuclear) PDFs of different flavours.
%
We find that the inclusion of systematic uncertainties does not significantly modify the
impact of these structure function measurements on the PDFs as compared
to an analysis that considers only statistical errors, unless extreme assumptions on the bin-by-bin
correlation model are adopted.
%
We illustrate the impact that the expected improvements on the (nuclear) PDFs provided 
on LHC neutrinos may have on precision measurements at the HL-LHC.
%
Our analysis demonstrates that detection and analysis of LHC far-forward neutrinos  effectively
extends the LHC with a charged-current counterpart of the
US-based Electron-Ion Collider (EIC)~\cite{AbdulKhalek:2021gbh}
with comparable kinematic reach, therefore realising a ``Neutrino-Ion Collider'' at CERN
without the need of additional accelerator infrastructure.

The outline of this paper is as follows.
%
First of all, in Sect.~\ref{sec:dis_pseudodata} we describe the procedure
adopted to generate projections for DIS structure functions associated to
LHC neutrino scattering, including the modelling of experimental systematic
uncertainties.
%
Then in Sect.~\ref{sec:settings} we discuss the theoretical settings used
for the calculation of DIS structure functions and the methodology adopted
to account for the constraints of LHC neutrino DIS data on proton and nuclear PDFs.
%
The projected impact of these structure functions on proton and nuclear
PDFs is quantified in Sects.~\ref{sec:protonPDFs} and~\ref{sec:nuclearPDFs} respectively.
%
Finally we summarise in Sect.~\ref{sec:summary} and consider some possible
directions for follow-up research.
